TBD

### 2021-02-14 outputs/paper/paper.Rmd
Add sampling simulation for Q1
Update sampling simulation

```{r, echo = FALSE}
print(dfBoroughs$prop)
```

>>>>

```{r, echo = FALSE}
#### Sampling Simulation ####

set.seed(853)

### Questions
# Q1: What region is your restaurant located in?
# Q2: What best describes the scale of your restaurant?
# Q3: What best describes your restaurant segmentation?
# Q4: How many years has your restaurant been in operation?
# Q5: Prior to (intervention start date), how many people did you employ?
# Q6: How many people do you currently employ?

sample_size <- 200

simulated_dataset_treated <- 
  tibble(
    type = rep("Treated", sample_size),
    Q1 = sample(x = c(
      "Downtown Toronto",
      "North York",
      "Scarborough",
      "West Toronto",
      "Etobicoke",
      "York",
      "Central Toronto",
      "East Toronto",
      "East York",
      "Other"),
      size = sample_size,
      replace = TRUE, 
      prob = c(0.28, 0.16, 0.14, 0.11, 0.09, 0.06, 0.06, 0.06, 0.04, 0)
    ),
    Q2 = sample(x = c(
      "Small",
      "Medium",
      "Large"),
      size = sample_size,
      replace = TRUE, 
      prob = c(0.15, 0.50, 0.35)
    ),
    Q3 = sample(x = c(
      "Fast-food/quick service",
      "Casual Dining",
      "Fine Dining",
      "Other"),
      size = sample_size,
      replace = TRUE, 
      prob = c(0.45, 0.20, 0.10, 0.25)
    ),
    Q4 = sample(x = c(
      "1-4 years",
      "5-7 years",
      "8-10 years",
      "10 or more years"),
      size = sample_size,
      replace = TRUE, 
      prob = c(0.40, 0.25, 0.20, 0.15)
    ),
    Q5 = rpois(n = sample_size, lambda = 30),
    Q6 = rpois(n = sample_size, lambda = 15),
  )

```
